Blog Post 5: The Value of Cross Validation & Hyperparameter Tuning

### 2020-10-08 Adler_personal/Blog5.Rmd
More stable this way somehow

```{r prepareData}
library(caret)
data(cars)
set.seed(84)
futIDX <- createDataPartition(cars$Price, p = 0.25)$Resample1
futDat <- cars[futIDX, ]
curDat <- cars[-futIDX, ]
tstIDX <- createDataPartition(curDat$Price[-futIDX], p = 0.3)$Resample1
trnDat <- curDat[-tstIDX, ]
tstDat <- curDat[tstIDX, ]
```

>>>>

```{r prepareData}
library(caret)
data(cars)
set.seed(84)
futIDX <- createDataPartition(cars$Price, p = 0.25)$Resample1
futDat <- cars[futIDX, ]
curDat <- cars[-futIDX, ]
trnIDX <- createDataPartition(curDat$Price, p = 0.7)$Resample1
trnDat <- curDat[trnIDX, ]
tstDat <- curDat[-trnIDX, ]
```
